\documentclass{article}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}

\usepackage{apacite}
\usepackage[sort, numbers]{natbib}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{lineno}
\linenumbers

\title{RSE-ops: Fostering Culture for Collaboration in Research Software Engineering}

\author{
  Sochat, Vanessa\\
  \and
  Gamblin, Todd\\
  \and
  Add your name here!
}

\begin{document}
\newgeometry{left=5cm,bottom=3cm,top=5cm,right=5cm}
\maketitle

\section{Abstract}
\input{abstract}
\input{introduction}
\input{what-is-devops}
\input{what-is-rseops}

\input{comparison}

\subsection{Accessibility for RSE-ops vs. DevOps}
\input{accessibility}

\subsection{Maintenance for RSE-ops vs. DevOps}
\input{maintenance}

\subsection{Scientific Software for RSE-ops vs. DevOps}
\input{scientific-software}

\subsection{Testing for RSE-ops vs. DevOps}
\input{testing}

\subsection{Scaling for RSE-ops vs. DevOps}
\input{scaling}

\subsection{Software Distribution for RSE-ops vs. DevOps}
\input{distribution}

\subsection{Dependency Management for RSE-ops vs. DevOps}
\input{dependencies}

\subsection{Permissions for RSE-ops vs. DevOps}
\input{permissions}

\subsection{Portability for RSE-ops vs DevOps}
\input{portability}

\subsection{Community standards for RSE-ops vs. DevOps}
\input{standards}

\subsection{Continuous Integration for RSE-ops vs. DevOps}
\input{continuous-integration}

\subsection{Continuous Deployment for RSE-ops vs. DevOps}
\input{continuous-deployment}

\subsection{Monitoring for RSE-ops vs. DevOps}
\input{monitoring}

\subsection{Security for RSE-ops vs. DevOps}
\input{security}

\input{summary-table}

\section{Why can't RSE-ops follow DevOps?}
\input{follow-devops}

\section{Informing one another: metadata for containers}
\input{containers}
\input{culture}
\input{mapping-space}

\section{Summary of Opportunities}
\input{summary-opportunities}

\section{References}
\setcitestyle{square}
\bibliographystyle{apacite}
\bibliography{rseops}

\end{document}
